

---
title: "plotly"
output: 
  html_document:
    toc: true
    toc_float: true
    navbar:
      - { icon: fa-home, href: index.html, align: right }
      
      - { icon: fa-envelope, href: mailto:<kz2383@cumc.columbia.edu>, align: right }
      - { icon: fa-github, href: https://github.com/zhankkk/, align: right }
    source_code: embed
    theme: 
      bootswatch: cerulean
---


This page will display some plotly plots based on specific dataset. 

# plotly plots


[plotly](plotly.html)


# load datasets



Tidy the dataset by selecting variables needed and restrict order number to a ramge of 5 to 60. 
```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
library(flexdashboard)
```
```{r}
data("instacart")

instacart = 
  instacart%>% 
  janitor::clean_names()%>%
  select(
    product_id,product_name,order_number, order_hour_of_day, department) %>%
    filter(order_number %in% 5:60)
  

```

Displaying order number distribution of products based on department applying boxplot
```{r}
instacart %>% 
  plot_ly(y = ~order_number, color = ~department, type = "box", colors = "viridis")


```
scatter plot for order number during different hour of the day 
```{r}
instacart %>%
  filter(department %in% c("beverage","frozen"))%>%
  plot_ly(
    x = ~order_hour_of_day, y = ~order_number, type = "scatter", mode = "markers",
    color = ~department, alpha = 0.3)
```

bar chart showing order count distribution for  snacks based on product name
```{r}
 instacart %>% 
  filter(department %in% c("snacks"))%>%
  plot_ly(x = ~product_name, y = ~order_number, type = 'bar')
```


